Effects of CHILDREN's programs

### 2020-02-27 paper.Rnw
update rnw

# <<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
# 
# # first, read in all Rds objects that you need
# 
# fundamental_dynamics = readRDS("./ANALYSIS/Tables/fundamental_dynamics.Rds")
#  
# colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
# 
# fundamental_dynamics <- xtable(fundamental_dynamics,
#                                digits = c(0, 0, 1, 1, 0, 0),
#           caption = "Summary Statistics",
#           align = "lmmmmm", 
#           label = "fundamentalDynamics"
#           )
# print(fundamental_dynamics, include.rownames = FALSE)
# @

@@

\begin{table}
\begin{center}
\begin{tabular}{l c}
\hline
 & Selfworth \\
\hline
(Intercept)             & $-1.13^{***}$ \\
                        & $(0.32)$      \\
dfcEF2$treatEF          & $-0.47$       \\
                        & $(0.31)$      \\
\hline
Num. obs.               & $430$         \\
R$^2$ (full model)      & $0.47$        \\
R$^2$ (proj model)      & $0.47$        \\
Adj. R$^2$ (full model) & $0.36$        \\
Adj. R$^2$ (proj model) & $0.36$        \\
\hline
\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
\end{tabular}
\caption{linear regression}
\label{table:coefficients}
\end{center}
\end{table}

@@

% #normal weights selfworth& subsidiy
% <<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
% 
% lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
% lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
% ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
% td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
% sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
% dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
% tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
% tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
% @

@@

#normal weights selfworth& subsidiy
<<equality_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=

>>>>

<<FundamentalDynamicsTest, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
# 
# # first, read in all Rds objects that you need
# 
# fundamental_dynamics = readRDS("./ANALYSIS/Tables/fundamental_dynamics.Rds")
#  
# colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
# 
# fundamental_dynamics <- xtable(fundamental_dynamics,
#                                digits = c(0, 0, 1, 1, 0, 0),
#           caption = "Summary Statistics",
#           align = "lmmmmm", 
#           label = "fundamentalDynamics"
#           )
# print(fundamental_dynamics, include.rownames = FALSE)
@

@@

% \begin{table}
% \begin{center}
% \begin{tabular}{l c}
% \hline
%  & Selfworth \\
% \hline
% (Intercept)             & $-1.13^{***}$ \\
%                         & $(0.32)$      \\
% dfcEF2$treatEF          & $-0.47$       \\
%                         & $(0.31)$      \\
% \hline
% Num. obs.               & $430$         \\
% R$^2$ (full model)      & $0.47$        \\
% R$^2$ (proj model)      & $0.47$        \\
% Adj. R$^2$ (full model) & $0.36$        \\
% Adj. R$^2$ (proj model) & $0.36$        \\
% \hline
% \multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
% \end{tabular}
% \caption{linear regression}
% \label{table:coefficients}
% \end{center}
% \end{table}

@@

% <<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
% 
% lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
% lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
% ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
% td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
% sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
% dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
% tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
% tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
% @

@@

<<equality_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
